%====================
% EXPERIENCE A
%====================
\subsection{{Full-Stack Developer \hfill Jun 2019 --- Present}}
\subtext{Tata Consultancy Services \hfill Bengaluru, Karnataka}
\subtext{Client: Commonwealth bank of Australia, CBA}
\begin{zitemize}
\item Developed testable web applications using React, Redux, and ASP.NET.

\item Created website layouts/user interfaces using HTML and CSS/Sass

\item Implemented RESTful API services using ASP.NET
   Core.

\item Integrated data from various back-end services.

\item Gathered and analyzed user specifications and software requirements to determine technical needs and design feasibility within time and cost constraint\item Provide accurate estimates for the development effort for new features.

\item Created prototypes and participated in PoC developments.

\item Assisted in A/B testing of different UX components.

\item Cooperated with web designers to match visual design intent

\item Mentored junior developers and helped new hires onboard and be successful.

\item Integrated Checkmarx SAST tools into TeamCity builds, which helped in identifying and resolving vulnerabilities.

\item Performed code reviews for other team members.

\item Participated in support and technical troubleshooting activity

\item Collaborate within the team to apply the principles of design, development, testing, deployment, support, and evaluation

\item Develop high-quality software solutions with comprehensive test coverage.

\item Analyze business objectives and translate requirements to technical implementation components.

\item Release and deployment
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Front-End Developer \hfill Dec 2016 --- Jun 2019}}
\subtext{Tata Consultancy Services \hfill Kolkata, West Bengal}
\subtext{Client: Alcoa and Arconic}
\begin{zitemize}
\item Worked in a team of 8 to develop responsive and cross-browser compatible web applications using AngularJS, JavaScript, HTML, and CSS.

\item Wrote unit tests to ensure code was bug-free. Also improved code coverage by 20%.

\item Handled client-side validations and errors.

\item Worked in an Agile, collaborative environment to develop web applications.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
